Data Analysis Expanded

### 2019-08-22 data_analysis/data_analysis_expanded.Rmd
another update

@@

@@

```{r s3_m2_b}
# narrow lambda, more starts:
set.seed(23439)
s3_m2_b <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "neg_unreg_like",
                              partitions = 5,
                              lambda_vec = seq(0,300,by=20),
                              multiplier = 200,
                              c_seq_len = 20,
                              starts = big_starts)
```
```{r s3_m2_b_print, results = 'asis'}
s3_m2_b %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br>
<br><br>

@@

@@

@@

>>>>

```{r s1_m2_c}
set.seed(4439)
s1_m2_c <- rre::cv_replicates(list_of_samples[[1]],
                              eval_function = "neg_unreg_like",
                              partitions = 5,
                              lambda_vec = seq(150,250,by=5),
                              multiplier = 200,
                              c_seq_len = 200,
                              starts = data.frame(alpha = 0.001879,
                                                  delta = 0.002208))
```
```{r s1_m2_c_print, results = 'asis'}
s1_m2_c %>% report_results_2(., list_of_samples[[1]], report_eta = T)
```
<br><br>

@@

```{r s2_m2_c}
# narrow lambda, more starts:
set.seed(12044)
s2_m2_c <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "neg_unreg_like",
                              partitions = 5,
                              lambda_vec = seq(0,100,by=5),
                              multiplier = 200,
                              c_seq_len = 200,
                              starts = data.frame(alpha = 0.002191,
                                                  delta = 0.002789))
```
```{r s2_m2_c_print, results = 'asis'}
s2_m2_c %>% report_results_2(., list_of_samples[[2]], report_eta = T)
```
<br><br>

@@

```{r s3_m2_b}
# narrow lambda, more starts:
set.seed(23439)
s3_m2_b <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "neg_unreg_like",
                              partitions = 5,
                              lambda_vec = seq(0,300,by=20),
                              multiplier = 200,
                              c_seq_len = 20,
                              starts = big_starts)
```
```{r s3_m2_b_print, results = 'asis'}
s3_m2_b %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br>

```{r s3_m2_c}
# narrow lambda, more starts:
set.seed(23444)
s3_m2_c <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "neg_unreg_like",
                              partitions = 5,
                              lambda_vec = seq(0,100,by=5),
                              multiplier = 200,
                              c_seq_len = 200,
                              starts = data.frame(alpha = 0.005138,
                                                  delta = 0.002135))
```
```{r s3_m2_c_print, results = 'asis'}
s3_m2_c %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
<br><br>

_Note_ The 'c' round of method 2 took over a day to run for these 3 samples.

@@

```{r s1_m4_c}
set.seed(2423)
s1_m4_c <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(150,250,by=5),
                              multiplier = 200,
                              c_seq_len = 200,
                              starts = data.frame(alpha = 0.005779,
                                                  delta = 0.002530))
```
```{r s1_m4_c_print, results = 'asis'}
s1_m4_c %>% report_results_2(., list_of_samples[[1]], report_eta = T)
```

@@

```{r s2_m4_c}
set.seed(23451)
s2_m4_c <- rre::cv_replicates(list_of_samples[[2]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,100,by=5),
                              multiplier = 200,
                              c_seq_len = 200,
                              starts = data.frame(alpha = 0.0016934,
                                                  delta = 0.0027209))
```
```{r s2_m4_c_print, results = 'asis'}
s2_m4_c%>% report_results_2(., list_of_samples[[2]], report_eta = T)
```

@@

```{r s3_m4_c}
# big grids and few partitions to start:
set.seed(7654)
s3_m4_c <- rre::cv_replicates(list_of_samples[[3]],
                              eval_function = "gof_chi_sq",
                              partitions = 5,
                              lambda_vec = seq(0,120,by=5),
                              multiplier = 200,
                              c_seq_len = 200,
                              starts = data.frame(alpha = 0.002450,
                                                  delta = 0.001773))
```
```{r s3_m4_c_print, results = 'asis'}
s3_m4_c %>% report_results_2(., list_of_samples[[3]], report_eta = T)
```
